Response to Pachter's Review

### 2020-01-22 index.Rmd
typo

In this analysis, we have addressed most of the criticisms in Pachter's review, acknowledging our errors when pointed, while rejecting his false claim that age was the greates confounder. The only one we have not addressed is his point that, "several p-values are computed and reported without any multiple testing correction." After consultation with a respected statistician, we do not see what the issue is. We reported every p-value and he is welcome to change the set.seed in our code, which he applauds us as easily reproducible.

>>>>

In this analysis, we have addressed most of the criticisms in Pachter's review, acknowledging our errors when pointed, while rejecting his false claim that age was the greatest confounder. The only one we have not addressed is his point that, "several p-values are computed and reported without any multiple testing correction." After consultation with a respected statistician, we do not see what the issue is. We reported every p-value and he is welcome to change the set.seed in our code, which he applauds us as easily reproducible.

### 2020-01-22 index.tex
typo
minor bug addressed mean calc

We calculate the average citations/average year since PhD of letters A,
B, and C, and compare them to our ranked list.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  For letter A - 15.98726
\item
  For letter B - 41.86467
\item
  For letter C - 55.3615
\end{enumerate}

@@

In this analysis, we have addressed most of the criticisms in Pachter's
review, acknowledging our errors when pointed, while rejecting his false
claim that age was the greates confounder. The only one we have not
addressed is his point that, ``several p-values are computed and
reported without any multiple testing correction.'' After consultation
with a respected statistician, we do not see what the issue is. We
reported every p-value and he is welcome to change the set.seed in our
code, which he applauds us as easily reproducible.

>>>>

We calculate the average citations per year since PhD of letters A, B,
and C, and compare them to our ranked list.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  For letter A - 15.98726
\item
  For letter B - 41.12345
\item
  For letter C - 55.5451
\end{enumerate}

@@

In this analysis, we have addressed most of the criticisms in Pachter's
review, acknowledging our errors when pointed, while rejecting his false
claim that age was the greatest confounder. The only one we have not
addressed is his point that, ``several p-values are computed and
reported without any multiple testing correction.'' After consultation
with a respected statistician, we do not see what the issue is. We
reported every p-value and he is welcome to change the set.seed in our
code, which he applauds us as easily reproducible.
